\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item[$\circ$]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% RESUME STARTS HERE
\begin{document}

\begin{center}
\textbf{\Huge \scshape Piss Fuck} \\ 
\small 734-787-8832 $\mid$ \href{mailto:ryankima@umich.edu}{\underline{ryankima@umich.edu}} $\mid$ \href{https://linkedin.com/in/ryankima}{\underline{linkedin.com/in/ryankima}} $\mid$ \href{https://github.com/ryankima}{\underline{github.com/ryankima}}
\end{center}

% EDUCATION
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Michigan State University}{East Lansing, MI}
{Bachelor of Science in Bartending, Minor in Being Unpleasant; GPA: 2.7}{Aug. 2021 - Present (Expected Graduation: May 2025)}
\resumeItemListStart
\resumeItem{Coursework: Food and Beverage Management, Mixology, Customer Relations, Event Planning, Business Finance.}
\resumeItem{Currently pursuing with an expected graduation date of May 2025.}
\resumeItemListEnd
\resumeSubheading
{Technische Universität Berlin}{Berlin, Germany}
{Study Abroad; International Laboratory Experience in Robotics Programming}{May 2022 - Jun. 2022}
\resumeItemListEnd

% EXPERIENCE
\section{Experience}

\resumeSubHeadingListStart
\resumeSubheading
{Engineering Development Group Intern}{Natick, MA}
{The Mathworks}{May 2023 - Aug 2023}
\resumeItemListStart
\resumeItem{Pioneered a code-generation pipeline permitting GPU hardware acceleration through Vulkan, resulting in 2x speed-ups in matrix operations with generated compute shaders; deployed open-source software to trim development time and introduce novel code optimizations.}
\resumeItem{Expanded GPU acceleration code generation to target additional hardware platforms through using IREE; created MLIR conversion passes to convert internal code generated intermediate representation, enabling the utilization of pretrained third party machine learning models.}
\resumeItemListEnd

\resumeSubheading
{Student Fellow}{Ann Arbor, MI}
{Consortium for Monitoring, Technology, and Verification - University of Michigan}{Jun 2022 - May 2023}
\resumeItemListStart
\resumeItem{Revamped software architecture for low-cost Geiger Counter, resulting in improved hardware performance, increased device compatibility, and reduced future maintenance requirements.}
\resumeItem{Developed software for Raspberry Pi sensors for environmental radiation monitoring; created custom wiring harnessing to connect sensors with custom PCB, improving vibration safety, durability, and maintenance ease; identified PCB design flaws for future revisions.}
\resumeItemListEnd

\resumeSubheading
{Instructional Assistant}{Ann Arbor, MI}
{University of Michigan}{Aug 2022 - Dec 2022}
\resumeItemListStart
\resumeItem{Devised course materials for introductory engineering concepts focusing on electrical engineering, radiation science, and radiation detection; fostered a safe, team-focused learning environment.}
\resumeItem{Ensured safety compliance for students handling radiological sources through lesson planning, personal protective equipment, and lab execution; analyzed and optimized the circuit design of class-made Geiger counter by tuning software to heighten the device’s radiation sensitivity.}
\resumeItemListEnd

\resumeSubheading
{Assistant in Research}{Ann Arbor, MI}
{University of Michigan}{Sep 2021 - May 2022}
\resumeItemListStart
\resumeItem{Developed firmware for custom sensors connected to an autonomous drone running PX4 autopilot, employing reliable communication protocols such as SPI and UART.}
\resumeItem{Performed design analysis to balance the weight and power of system computers for aerial drone applications with the required computational strength; created a hardware development environment to swiftly test communication protocols and boards.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% SKILLS
\section{Skills}
\resumeSubHeadingListStart
\item\small{
     \textbf{Languages:} C/C++, Python, Java, HTML5, CSS, JavaScript, C\#, SQL, Matlab \\
     \textbf{Tools:} XCode, Visual Studio, Git, Github, CAD, Raspberry Pi, SolidWorks, MySQL, MongoDB, Android Studio, Flask, IREE, MLIR, Vulkan, GPU, Compilers}
\resumeSubHeadingListEnd

%-------------------------------------------  
\end{document}