\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item[$\circ$]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% RESUME STARTS HERE

\begin{document}
\begin{center}
	\textbf{\Huge \scshape Ava Torres} \\ \vspace{1pt}
	\small 734-787-8832 $|$ \href{mailto:ryankima@umich.edu}{\underline{ryankima@umich.edu}} $|$ 
	\href{https://linkedin.com/ryankima}{\underline{linkedin.com/ryankima}} $|$
	\href{https://github.com/ryankima}{\underline{github.com/ryankima}}
\end{center}

%---EDUCATION---
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Michigan State Univeristy}{East Lansing, MI}
{Bachelor of Bartending, Minor in being unpleasant; GPA: 2.7}{August 2021 - Present | Expected Graduation: May 2025}
\resumeItemListStart
\resumeItem{Coursework: Advanced Mixology, Spirits and Liqueurs Analysis, Beverage Management, Beverage Marketing, Craft Beer and Brewing, Wines and Vintages, Bar Operations and Control, Customer Service Essentials.}
\resumeItemListEnd

\resumeSubheading
{Technische Universität Berlin}{Berlin, Germany}
{Study Abroad; International laboratory experience in robotics programming }{May 2022 - June 2022}
\resumeSubHeadingListEnd

%---EXPERIENCE---
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Engineering Development Group Intern}{Natick, MA}
{The Mathworks}{May 2023 - Aug 2023}
\resumeItemListStart
\resumeItem{Pioneered a code generation pipeline for GPU hardware acceleration, achieving 2x speed-ups in matrix operations; the pipeline was built with Vulkan and compute shaders; these optimizations reduced future development time significantly.}
\resumeItem{Expanded the GPU acceleration code generation to target additional hardware platforms using IREE, thereby broadening the reach and efficacy of the technology.}
\resumeItem{Developed MLIR conversion passes to convert internal code generated intermediate representation allowing for the utilization of pre-trained third-party machine learning models thereby improving model adaptability and utility.}
\resumeItemListEnd

\resumeSubheading
{Student Fellow in Monitoring, Technology, and Verification}{Ann Arbor, MI}
{Consortium for Monitoring - University of Michigan}{Jun 2022 - May 2023}
\resumeItemListStart
\resumeItem{Overhauled an existing software architecture for a low-cost Geiger Counter, leading to increased hardware performance, improved device compatibility, and lowering potential maintenance requirements.}
\resumeItem{Developed software for reading sensor data from Raspberry Pi geared towards environmental radiation monitoring; at the same time, ensured robustness for different sensor hardware.}
\resumeItem{Identified design flaws and gave proposals for design improvements thereby enabling future enhancements in PCB performance.}
\resumeItem{Developed and delivered presentations at national conferences effectively conveying the essence of the research findings.}
\resumeItemListEnd

\resumeSubheading
{Instructional Assistant}{Ann Arbor, MI}
{University of Michigan}{Aug 2022 - Dec 2022}
\resumeItemListStart
\resumeItem{Developed course lessons for introductory engineering to effectively teach concepts of introductory electrical engineering, radiation science, and radiation detection in a collaborative environment.}
\resumeItem{Ensured safety compliance of the students handling radiological sources by managing lesson planning, personal protective equipment, and overseeing execution of labs.}
\resumeItem{Analyzed and improved the circuit design of a Geiger counter made in the class by adjusting low-pass filter values and tuning software, ultimately increasing the device's sensitivity to radiation.}
\resumeItemListEnd

\resumeSubheading
{Assistant in Research}{Ann Arbor, MI}
{University of Michigan}{Sep 2021 - May 2022}
\resumeItemListStart
\resumeItem{Developed firmware for custom sensors connected to an autonomous drone running PX4 autopilot utilizing reliable communication protocols using SPI and UART.}
\resumeItem{Performed design analysis to balance weight and power of the system computers for aerial drone applications, ensuring optimal computational strength and efficiency.}
\resumeItem{Created a custom hardware development environment to test communication protocols and boards rapidly, reducing testing time and increasing productivity.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%---SKILLS---
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\textbf{Languages}{: C/C++, Python, Java, HTML5, CSS, JavaScript, C\#, SQL, Matlab} \\
		\textbf{Tools}{: XCode, Visual Studio, Git, Github, Computer-aided Design (CAD), Raspberry Pi, SolidWorks, MySQL, MongoDB, Android Studio, Flask, IREE, MLIR, Vulkan, GPU, Compilers} \\
	}}
\end{itemize}

\end{document}