dd------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------


% only three bullet points man. you really need to work on this.

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item[$\circ$]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{center}
	\textbf{\Huge \scshape Benjamin Datsko} \\ \vspace{1pt}
	\small (248) 909-5982 $|$ \href{mailto:bdatsko@umich.edu}{\underline{bdatsko@umich.edu}} $|$ 
	\href{https://linkedin.com/in/bendatsko/}{\underline{linkedin.com/in/bendatsko}} $|$
	\href{https://github.com/bendatsko}{\underline{github.com/bendatsko}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Michigan -- College of Engineering}{Ann Arbor, MI}
{Bachelor of Science and Engineering in Computer Science, Electrical Engineering Minor}{Aug. 2021 - Apr. 2025}
\resumeItemListStart
\resumeItem{Courses: CS Theory, Computational Linear Algebra, Data Structures and Algorithms, Discrete Mathematics.}

\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCe-----------
\section{Experience \scriptsize \scshape [SEE MORE AT \href{https://datsko.dev/projects}{\underline{DATSKO.DEV}}]}
 
\resumeSubHeadingListStart
\resumeSubheading
{Undergraduate Research Scientist}{Ann Arbor, MI}
{Michigan Integrated Circuits Laboratory -- Flynn Research Group}{Aug. 2022 -- Present}
\resumeItemListStart
\resumeItem{Created low-noise power supply for integrated circuits testing leveraging LiPo battery cells; added comprehensive battery management system into C++-based real-time operating system; achieved signal clarity 2x cleaner than industry-grade power supplies for half the cost.}
\resumeItem{Formulated 130,000-parameter computational neural network using PyTorch for real-time object recognition to test model-on-chip RISC-V machine learning accelerator (ASIC). \textbf{Pending IEEE journal publication.}}
\resumeItem{Overhauled 40-GHz modulated RF signal source using high-resolution DAC, FPGA, and up-converter; leveraged MATLAB to produce circular single-tone, QAM, etc., sequences run on FPGA (configured in SystemVerilog).}
\resumeItem{Revised multi-axis high-torque motor control calibration system for over-the-air testing of 64-element 28-GHz digital beamformer with MATLAB and Raspberry Pi. Designed, tested, and assembled two-sided motherboard interfacing with Kintex RF FPGA; implemented beamforming algorithm in VHDL. \textbf{Pending IEEE journal publication.}}
\resumeItemListEnd

\resumeSubheading
{Strategy/Software Engineer}{Ann Arbor, MI}
{University of Michigan Solar Car Team}{Aug. 2022 -- Present}
{\textbf{}}{}
\resumeItemListStart
\resumeItem{Led project combining the University of Michigan Solar Car's four distinct simulators (C++ race simulator, Java fluid dynamics simulator, Unity vehicle dynamics simulator, and Python weather simulator) into web application.}
\resumeItem{Built a React front-end (using OAuth 2.0), four Flask-based simulator APIs, and an EJS REST API for interfacing with MongoDB container (Docker) to link user data to raw simulation output and statistical analysis results.}          
\resumeItemListEnd

\resumeSubheading
{Gators STR Swim Team Head Coach}{Oxford, MI}
{USA Swimming}{Apr. 2021 -- Sep. 2022}
\resumeItemListStart
\resumeItem{Created training regimen and supervised training sessions, providing direct feedback to $\sim$250 athletes.}
\resumeItem{Evaluated the effectiveness of programming through statistical analysis, witnessing growth in 90\% of athletes.}
\resumeItemListEnd

\resumeSubheading
{Information Technology Intern}{Flint, MI}
{Hurley Medical Center - Main Campus}{Jun. 2021 -- Aug. 2021}
\resumeItemListStart
\resumeItem{Devised Shell scripts to automate disk encryption and perform proprietary operating system cloning.}
\resumeItem{Performed hardware and software-level maintenance on medical devices, servers, and workstations.}
\resumeItemListEnd
\resumeSubHeadingListEnd
  

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{High-Altitude Payload for UV Radiation Detection} $|$ \emph{Arduino, Altium Designer}}{}
\resumeItemListStart
\resumeItem{Engineered weather balloon payload system to conduct UV radiation intensity measurements at altitudes of 86,000 feet; data analysis provided crucial insights into long-term ozone degradation trends in southeast Michigan.}
\resumeItem{Wrote C firmware based on Super-Loop architecture to gather GPS and sensor data and Python script to parse GPS NMEA strings, extract waypoint data, and plot 42-mile-long flight path (using Google Maps API).}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{Pathfinding Algorithm Visualizer} $|$ \emph{Javascript, Adobe XD}}{}
\resumeItemListStart
\resumeItem{Constructed a web application for visualizing four pathfinding algorithms (A*, Dijkstra's, BFS, and DFS) incorporating real-time start/end point editing and obstacle drawing with cursor; written in Vanilla JavaScript.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{Microsoft Partner, Realms Contributor} $|$ \emph{Java, Adobe Creative Cloud, Blender}}{}
\resumeItemListStart
\resumeItem{Developed three licensed games for Minecraft Realms -- \emph{The Missing Sandwich}, \emph{Annoying Ghosts}, and \emph{Witchcraft and Wizardry} -- utilizing Java, Adobe Creative Cloud, Blender; led team of six; garnered 600,000+ downloads.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\textbf{Languages}{: C, C++, C\#, Java, JavaScript, Unix, Python, Django, Swift, Rust, MySQL, NoSQL, Verilog, RTOS.} \\
		\textbf{Technologies}{: Flask, Git, GraphQL, Kubernetes, LIDAR (feedback control), Machine Learning (OpenCV, PyTorch), Matplotlib, Node, NumPy, React, SCSS, TailwindCSS, WordPress, Azure, GSuite, Microsoft 365, Inventor, Altium.} \\
        \textbf{Extracurriculars}{: U-M Club Swim Team, U-M Climbing Team, U-M Solar Car Team, U-M Rocketry Club (MASA).} \\
	}}
\end{itemize}


%-------------------------------------------
\end{document}